---
title: "ADMB-TMB Installation Instructions"
author: "Charlie Belinsky"
quarto.css: https://cdn.jsdelivr.net/gh/QFCatMSU/OnlineClassBackEnd/module.css
format: gfm
---

```{=html}
<style>
  /* Custom CSS styles */
  p, ul, ol {
    margin-top: 0 !important;
    margin-bottom: 0 !important;
    padding-top: 0 !important;
    padding-bottom: 0 !important;
  }
</style>
```
## 2 - Overview

These procedures in the document install the following software and was tested on 8/30/22:

-   R 4.2.1

-   Rtools 4.2 (for the CPP compilers)

-   RStudio 2022.07.1 Build 554

-   TMB package for R 1.9.1

-   ADMB 13.0 - Emacs 27.2 (*Emacs version 28 does not work*)

    -   Emacs configuration files - These files provide the syntax highlighting in Emacs for both ADMB and TMB and set up the Environment

-   admb2r.cpp in the ADMB folder

### Admin access to your computer

-   The installation procedures will do the following that might require administrative access to your computer:

-   Install programs (R, RStudio, Rtools, ADMB, Emacs)

-   Install programs directly to the C: drive (ADMB, RTools)

-   Change the User Environment variables (PATH.bat)

-   Install programs not validated by Microsoft (ADMB)

-   Run a batch file (PATH.bat)

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
